\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 trunk/europa.tex
updates on europa.tex for Javier

Most real-world planning problems need to deal with plans made up of
actions that typically depend upon limited resources (\eg fuel,
storage capacity, battery state of charge, data buffers).  \eu
provides built-in support for resource computation. In \eus
representation resource object types come in three forms with related
constraints. \textbf{Reservoir} resources can have both
\texttt{consume(resource,time,quantity)} and
\texttt{produce(resource,time,quantity)} constraints. Production and
consumption is instantaneous. \textbf{Reusable} resources have
\texttt{uses(resource,start,duration,quantity)} constraints that use a
quantity of the resource for a specific duration, which are then
released. \textbf {Unary} resources are reusable with capacity$ = 1$,
which allows \eu to perform run time savings in comparison to the
generic reusable class. Configuration options are offered such that in
addition to the usual constraint violations when a resource is
completely depleted, plan flaws can be generated whenever a resource
level is outside a specific upper or lower bound, or when
instantaneous production or consumption exceeds a specific threshold.

>>>>

Most real-world planning problems need to deal with plans made up of
actions that typically depend upon limited resources (\eg fuel,
storage capacity, battery state of charge, data buffers).  \eu
provides built-in support for resource computation. In \eus
representation resource object types come in three forms with related
constraints. \textbf{Reservoir} resources can have both
\texttt{consume(resource,time,quantity)} and
\texttt{produce(resource,time,quantity)} constraints; production and
consumption is instantaneous. \textbf{Reusable} resources on the other
hand, have constraints that use a quantity of the resource for a
specific duration (\texttt{uses(resource,start,duration,quantity)}),
which are then subsequently released. \textbf {Unary} resources are
reusable with capacity$ = 1$, which allows \eu to perform run time
savings in comparison to the generic reusable class. Configuration
options are offered such that in addition to the usual constraint
violations when a resource is completely depleted, plan flaws can be
generated whenever a resource level is outside a specific upper or
lower bound, or when instantaneous production or consumption exceeds a
specific threshold.
